Deciding Bitvector Termination with Program Synthesis

### 2014-07-02 papers/termination/paper.tex
prelim + sec 6

Given that our state space is finite, a transition relation induces a infinite execution if and only if some state is 
visited infinitely many times in the course of the execution. Hence, an alternative formulation of the non-termination problem 
for bit-vectors may search for singleton recurrence sets (the recurrence set contains only the state visited infinitely many times).
However, this would require reasoning about the transitive closure of the transition relation.\\

>>>>

Given that our state space is finite, a transition relation induces a infinite execution if and only if some state is 
visited twice in the course of the execution. Hence, an alternative formulation of the non-termination problem 
for bit-vectors may search for a state that is visited twice.
However, this would require reasoning about the transitive closure of the transition relation.\\
